Fast and Flexible Binary Instrumentation for the Kernel

### 2013-12-17 VEE-14/paper.tex
Working on lmbench evaluation charts.

\subsection{Optimizations}

@@

What has been evaluated:

\paragraph{lmbench}
\begin{itemize}
	\item Btkernel
	\item Granary, full-kernel, null
	\item Granary, full-kernel, even/odd
	\item Granary, full-kernel, even/odd, where even/odd is a runtime check and branch.
\end{itemize}

\paragraph{fileserver}
Setup: 1GB RAM, 3GB partition, ext3+jbd, >1GB mounted file system.
\begin{itemize}
	\item full-kernel
	\begin{itemize}
		\item Btkernel
		\item Granary, null
		\item Granary, even/odd
		\item Granary, even/odd, where even/odd is a runtime check and branch.
	\end{itemize}
	\item module-only, (ext3+jbd)
	\begin{itemize}
		\item Granary, null
		\item Granary, even/odd
		\item Granary, even/odd, where even/odd is a runtime check and branch.
	\end{itemize}
\end{itemize}

\paragraph{kernel compile}
Same as fileserver, but with 8GB RAM instead of 3GB.

\paragraph{recursive copy of kernel source tree}
Same as fileserver, but with 8GB RAM instead of 3GB.

>>>>

\subsection{Optimizations}\label{sec:optimize}

@@

\begin{figure*}
\centering\epsfig{file=charts/lmbench_legend.eps,height=6em} \\
\subfloat[Fast operations]{\epsfig{file=charts/lmbench_fast.eps,height=18em}}
\subfloat[Fork operations]{\epsfig{file=charts/lmbench_fork.eps,height=18em}}
\caption{Microbenchmark results from \texttt{lmbench} that shows the effect of Granary's code cache optimizations (\Cref{sec:optimize}).}
\end{figure*}
